\begin{deluxetable*}{lllcllcllcll}\label{tbl:spire_flux}
\tabletypesize{\scriptsize}
\tablewidth{0pt}
\tablecaption{SPIRE Flux Densities}
\tablehead{\colhead{Name} & \colhead{RA} & \colhead{DEC} & \colhead{$F_{250}$} & \colhead{Method$_{250}$} & \colhead{Flag$_{250}$} &\colhead{$F_{350}$} & \colhead{Method$_{350}$} & \colhead{Flag$_{350}$} &\colhead{$F_{500}$} & \colhead{Method$_{500}$} &\colhead{Flag$_{500}$}\\
\colhead{} & \colhead{J2000} & \colhead{J2000} & \colhead{(Jy)} & \colhead{} & \colhead{} & \colhead{(Jy)} & \colhead{} & \colhead{} & \colhead{(Jy)} \colhead{} & \colhead{}}
\startdata
Mrk 335	&	00h06m19.5s	&	+20d12m10s	&	$	0.068	\pm	0.007	$	&	TF	&	A	&	$		<	0.067	$	&	AP	&	U	&	$		<	0.078	$	&	AP	&	U	\\
2MASX J00253292+6821442	&	00h25m32.9s	&	+68d21m44s	&	$		<	0.286	$	&	AP	&	UC	&	$		<	0.364	$	&	AP	&	UC	&	$		<	0.263	$	&	AP	&	UC	\\
CGCG 535-012	&	00h36m21.0s	&	+45d39m54s	&	$	0.178	\pm	0.034	$	&	AP	&	A	&	$		<	0.140	$	&	AP	&	U	&	$	0.061	\pm	0.011	$	&	AP	&	A	\\
NGC 235A	&	00h42m52.8s	&	-23d32m28s	&	$	0.955	\pm	0.081	$	&	AP	&	A	&	$	0.399	\pm	0.060	$	&	AP	&	A	&	$		<	0.126	$	&	AP	&	U
\enddata
\tablecomments{\textit{Column 1:} Name of the source. \textit{Column 2:} Right ascension in J2000 coordinates. \textit{Column 3:} Declination in J2000 coordinates. \textit{Column 4:} 250 \um{} flux density and 1$\sigma$ uncertainty in units of Jy. 5$\sigma$ upper limits are given for undetected sources. \textit{Column 5:} Method used to extract the photometry. Either ``TF'' for timeline fitting or ``AP'' for aperture photometry. See text for details on the differences. \textit{Column 6:} Flag for the photometry. ``A'' = source was detected at greater than 5$\sigma$. ``U'' = 5$\sigma$ upper limit. ``C'' = likely foreground cirrus contamination. ``d'' = nearby companion however unlikely to affect photometry. ``D'' = nearby companion that is likely strongly affecting photometry. \textit{Columns 7--9:} Same as Columns 4--6 except for the 350 \um{} waveband. \textit{Columns 10--12:} Same as Columns 4--6 except for the 500 \um{} waveband. Full version of the table available in online version.}
\end{deluxetable*}

  
  
  
  
  