\subsubsection{SPIRE Colors}
While in the previous sections, we examined the absolute luminosities of each SPIRE waveband and the correlations between each other and other wavebands (PACS and BAT), in this section we examine the SPIRE colors (i.e. flux ratios). Colors in general provide measures of the shape of the SED. Different objects and mechanisms produce significantly different SED shapes across the same wavelength regime, therefore colors can be used to separate distinct populations from each other especially when groups display the same absolute brightnesses.

We investigate two colors, $F_{250}/F_{350}$ and $F_{350}/F_{500}$, that probe the Rayleigh Jeans tail of a modified blackbody if the dominant process producing the emission is cold dust. Figure~\ref{fig:hist_colors} plots the KDE of the two colors. The top row compares the distribution of the colors ($F_{250}/F_{350}$ on the left and $F_{350}/F_{500}$ on the right) from the BAT AGN and HRS samples. We also plot the theoretical color of the modified blackbody with a dust temperature of 20 K and emissivity ($\beta$) of 2.0, values typical of normal, star-forming galaxies \citep[e.g.][]{Calzetti:2000fk, Smith:2012fj, Galametz:2012uq, Dale:2012dq, Cortese:2014qq}. The HRS and BAT AGN seem to display very similar values for $F_{350}/F_{500}$ whereas the HRS is skewed toward lower values of $F_{250}/F_{350}$ compared to the BAT AGN. Results of a K-S test show that the HRS and BAT AGN $F_{350}/F_{500}$ colors are drawn from the same parent population with a $P_{K-S} = 0.28$ while the $F_{250}/F_{350}$ colors are significantly different ($P_{K-S} = 1 \times 10^{-4}$). 

In the bottom row, we compare Sy 1's and Sy 2's. Based on the results of our analysis in Section~\ref{sec:det_rate_lum_dist}, we would expect Sy 1's and Sy 2's to show the same distribution of colors. Indeed this is the case as both distributions in both colors peak at nearly the same values and have nearly the same spread. K-S tests reveal the colors for the two Seyfert types are drawn from the same parent population with $P_{K-S} = 0.2$ for $F_{250}/F_{350}$ and $P_{K-S} = 0.3$ for $F_{350}/F_{500}$.
  